\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed\footnotemark[2]

### 2015-09-07 paper/paper_methodology.tex
Added link to github repo in paper

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\section{Methodology}
\label{sec:methodology}

We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlying machine translations.
%
To test this hypothesis, we conduct a bilingual post-editing experiment where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.

>>>>

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode
\vspace{-1.5mm}
\section{Methodology}
\label{sec:methodology}
\vspace{-1.5mm}
We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlying machine translations.
%
To test this hypothesis, we conduct a bilingual post-editing experiment where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.

### 2015-09-07 paper/paper_results.tex
Added link to github repo in paper

Following the methodology outlined in \S\ref{sec:translation_quality}, all post-edited output as well as all machine translations were evaluated by bilingual human judges using the adequacy scales shown in Table~\ref{judge_guidelines} \vpageref{judge_guidelines}.

>>>>

Following the methodology outlined in \S\ref{sec:translation_quality}, all post-edited output as well as all machine translations were evaluated by bilingual human judges using the adequacy scales shown in Table~\ref{judge_guidelines}. % \vpageref{judge_guidelines}.
